07_summary_stats

### 2023-10-16 07_summary_stats.Rmd
Update 07_summary_stats.Rmd

@@

Read in RDS files of each buoy + all environ variables + AIS (pending)
```{r}
ftlist <- dir("data/", recursive=TRUE, full.names=TRUE, pattern="fulltrack")

for (ft in ftlist) {
  df <- readRDS(ft)
  assign(paste0("fulltrack", substr(ft, 15, 16)), df)
}
```

@@

Create df from 1 percentile
```{r}
# 1 Percentile
pct01_07 <- cbind(BB_pct01_07, TO_pct01_07) %>%
  select(., -3)
pct01_08 <- cbind(BB_pct01_08, TO_pct01_08) %>%
  select(., -3)
pct01_10 <- cbind(BB_pct01_10, TO_pct01_10) %>%
  select(., -3)
pct01_12 <- cbind(BB_pct01_12, TO_pct01_12) %>%
  select(., -3)
pct01_13 <- cbind(BB_pct01_13, TO_pct01_13) %>%
  select(., -3)
pct01_14 <- cbind(BB_pct01_14, TO_pct01_14) %>%
  select(., -3)
pct01_16 <- cbind(BB_pct01_16, TO_pct01_16) %>%
  select(., -3)
pct01_18 <- cbind(BB_pct01_18, TO_pct01_18) %>%
  select(., -3)
pct01_19 <- cbind(BB_pct01_19, TO_pct01_19) %>%
  select(., -3)
pct01_20 <- cbind(BB_pct01_20, TO_pct01_20) %>%
  select(., -3)
pct01_21 <- cbind(BB_pct01_21, TO_pct01_21) %>%
  select(., -3)
pct01_22 <- cbind(BB_pct01_22, TO_pct01_22) %>%
  select(., -3)
pct01_23 <- cbind(BB_pct01_23, TO_pct01_23) %>%
  select(., -3)

pct01_07$buoy <- ("07")
pct01_08$buoy <- ("08")
pct01_10$buoy <- ("10")
pct01_12$buoy <- ("12")
pct01_13$buoy <- ("13")
pct01_14$buoy <- ("14")
pct01_16$buoy <- ("16")
pct01_18$buoy <- ("18")
pct01_19$buoy <- ("19")
pct01_20$buoy <- ("20")
pct01_21$buoy <- ("21")
pct01_22$buoy <- ("22")
pct01_23$buoy <- ("23")

pct01_all <- rbind(pct01_07, pct01_08, pct01_10, pct01_12, pct01_13,
                   pct01_14, pct01_16, pct01_18, pct01_19, pct01_20,
                   pct01_21, pct01_22, pct01_23)

# Group by and summarize
pct01_all %>%
  group_by(buoy) %>%
  summarize(max(`TOL_125`))

Create df from 99 percentile
```{r}
# 99 Percentile
pct99_07 <- cbind(BB_pct99_07, TO_pct99_07) %>%
  select(., -3)
pct99_08 <- cbind(BB_pct99_08, TO_pct99_08) %>%
  select(., -3)
pct99_10 <- cbind(BB_pct99_10, TO_pct99_10) %>%
  select(., -3)
pct99_12 <- cbind(BB_pct99_12, TO_pct99_12) %>%
  select(., -3)
pct99_13 <- cbind(BB_pct99_13, TO_pct99_13) %>%
  select(., -3)
pct99_14 <- cbind(BB_pct99_14, TO_pct99_14) %>%
  select(., -3)
pct99_16 <- cbind(BB_pct99_16, TO_pct99_16) %>%
  select(., -3)
pct99_18 <- cbind(BB_pct99_18, TO_pct99_18) %>%
  select(., -3)
pct99_19 <- cbind(BB_pct99_19, TO_pct99_19) %>%
  select(., -3)
pct99_20 <- cbind(BB_pct99_20, TO_pct99_20) %>%
  select(., -3)
pct99_21 <- cbind(BB_pct99_21, TO_pct99_21) %>%
  select(., -3)
pct99_22 <- cbind(BB_pct99_22, TO_pct99_22) %>%
  select(., -3)
pct99_23 <- cbind(BB_pct99_23, TO_pct99_23) %>%
  select(., -3)

# Add column with buoy number
pct99_07$buoy <- ("07")
pct99_08$buoy <- ("08")
pct99_10$buoy <- ("10")
pct99_12$buoy <- ("12")
pct99_13$buoy <- ("13")
pct99_14$buoy <- ("14")
pct99_16$buoy <- ("16")
pct99_18$buoy <- ("18")
pct99_19$buoy <- ("19")
pct99_20$buoy <- ("20")
pct99_21$buoy <- ("21")
pct99_22$buoy <- ("22")
pct99_23$buoy <- ("23")

pct99_all <- rbind(pct99_07, pct99_08, pct99_10, pct99_12, pct99_13,
                   pct99_14, pct99_16, pct99_18, pct99_19, pct99_20,
                   pct99_21, pct99_22, pct99_23)
```

Plot 99pct and 1pct by buoy
```{r fig.height=5, fig.width=13}
# Group by and summarize
pct99_all %>%
  group_by(buoy) %>%
  summarize(max(`TOL_125`)) %>%
  ggplot(aes(x = buoy, y = `max(TOL_125)`)) + geom_bar(stat = "identity")

#TOL timeline by buoy
pct99_all %>%
  ggplot(aes(x = dateTime, y = TOL_2000, color = buoy)) + geom_line()

# Average dB by hour for each frequency
pct99_16 %>%
  group_by(time = floor_date(dateTime, "1 hour")) %>%
  summarize(mean_BB = mean(`BB_20-24000`),
            meanTOL_125 = mean(TOL_125),
            meanTOL_250 = mean(TOL_250),
            meanTOL_500 = mean(TOL_500),
            meanTOL_2000 = mean(TOL_2000),
            meanTOL_4000 = mean(TOL_4000),
            meanTOL_20000 = mean(TOL_20000)) %>%
  pivot_longer(cols = mean_BB:meanTOL_20000,
               names_to = "frequency",
               values_to="dB") %>%
  ggplot(aes(x = time, y = dB)) + geom_line(aes(color = frequency)) #+
  #geom_point(data = allDrifts, aes(color = species))
# Show more dates/times on x axis
# 99pct, buoy 16 has a strong peak later in journey at 4kHz

ggplot() +
  geom_point(data = pct01_23, aes(x = lubridate::round_date(dateTime, "2 hours"), y = TOL_125), color = 'steelblue') +
  #geom_line(data = pct99_23, aes(x = dateTime, y = TOL_125), color = 'coral') +
  facet_grid()

@@

Buoy 14 # Issue binding pct50 with others due to differing number of rows
```{r}
# Create columns with percentiles and BIND
pct50_14_select <- pct50_14 %>% select(UTC, TOL_125, TOL_2000) %>% 
  rename(pct50_TOL125 = TOL_125,
         pct50_TOL2000 = TOL_2000)
pct10_14_select <- pct10_14 %>% select(UTC, TOL_125, TOL_2000) %>%
   rename(pct10_TOL125 = TOL_125,
         pct10_TOL2000 = TOL_2000)
pct90_14_select <- pct90_14 %>% select(UTC, TOL_125, TOL_2000) %>%
   rename(pct90_TOL125 = TOL_125,
         pct90_TOL2000 = TOL_2000)

# Bind
#pct14 <- cbind(pct10_14_select, pct50_14_select, pct90_14_select)

@@

#Summarize
buoy23pctSummary <- pct23_whl %>%
  group_by(species) %>%
  summarize(pct10_125_mean = mean(pct10_TOL125),
            pct50_125_mean = mean(pct50_TOL125),
            pct90_125_mean = mean(pct90_TOL125),
            pct10_2000_mean = mean(pct10_TOL2000),
            pct50_2000_mean = mean(pct50_TOL2000),
            pct90_2000_mean = mean(pct90_TOL2000))
```

@@

## Buoy 14 ##
#kable(buoy14pctSummary, col.names = c("Animal", "10th", "Mean", "90th", "10th", "Mean", "90th"),
#                                     caption = "Summary Percentiles for Buoy 14") %>%
#  kableExtra::kable_classic() %>%
#  kableExtra::add_header_above(c(" " = 1, "TOL 125" = 3, "TOL 2000" = 3))

@@

pdf(paste("timeSeries8-31",".pdf"), width=14, height=10)

### Buoy 7 ####
W.07 <- fulltrack07 %>%
  select(UTC, BWpresence, species) %>%
  filter(species == "ZC")

@@

g1 <- (plotTimeseries(fulltrack07, column='TOL_125', bin='1hour', style = 'heatmap', title='Buoy 7: TOL 125 Plot + ZC'))
g2 <- plotPresGrid(W.07, bin = 'hour', type = 'presence', start = min(fulltrack07$UTC),
                         end = max(fulltrack07$UTC), fill = NA, color = "white")

@@

t1 <- plotTimeseries(fulltrack07, column='TOL_2000', bin='1hour', style = 'heatmap', title='Buoy 7: TOL 2000 Plot + ZC')
t2 <- plotPresGrid(W.07, bin = 'hour', type = 'presence', start = min(fulltrack07$UTC),
                         end = max(fulltrack07$UTC), fill = NA, color = "white")

@@

```{r fig.width=12}
###### Buoy 8 ####
W.08 <- fulltrack08 %>%
  select(UTC, BWpresence, species) %>%
  filter(species == "ZC")

@@

g1 <- (plotTimeseries(fulltrack08, column='TOL_125', bin='1hour', style = 'heatmap', title='Buoy 8: TOL 125 Plot + ZC'))
g2 <- plotPresGrid(W.08, bin = 'hour', type = 'presence', start = min(fulltrack08$UTC),
                         end = max(fulltrack08$UTC), fill = NA, color = "white")

combined.g <- g1
combined.g$layers <- c(combined.g$layers, g2$layers)
#####
t1 <- plotTimeseries(fulltrack08, column='TOL_2000', bin='1hour', style = 'heatmap', title='Buoy 8: TOL 2000 Plot + ZC')
t2 <- plotPresGrid(W.08, bin = 'hour', type = 'presence', start = min(fulltrack08$UTC),
                         end = max(fulltrack08$UTC), fill = NA, color = "white")

@@

W.10 <- fulltrack10 %>%
  select(UTC, BWpresence, species) %>%
  filter(species == "ZC")

@@

g1 <- (plotTimeseries(fulltrack10, column='TOL_125', bin='1hour', style = 'heatmap', title='Buoy 10: TOL 125 Plot + ZC'))
g2 <- plotPresGrid(W.10, bin = 'hour', type = 'presence', start = min(fulltrack10$UTC),
                         end = max(fulltrack10$UTC), fill = NA, color = "white")

combined.g <- g1
combined.g$layers <- c(combined.g$layers, g2$layers)
#####
t1 <- plotTimeseries(fulltrack10, column='TOL_2000', bin='1hour', style = 'heatmap', title='Buoy 10: TOL 2000 Plot + ZC')
t2 <- plotPresGrid(W.10, bin = 'hour', type = 'presence', start = min(fulltrack10$UTC),
                         end = max(fulltrack10$UTC), fill = NA, color = "white")

@@

```{r fig.width=12}
## Buoy 12
W.12 <- fulltrack12 %>%
  select(UTC, BWpresence, species) %>%
  filter(species == "ZC")

@@

g1 <- (plotTimeseries(fulltrack12, column='TOL_125', bin='1hour', style = 'heatmap', title='Buoy 12: TOL 125 Plot + ZC'))
g2 <- plotPresGrid(W.12, bin = 'hour', type = 'presence', start = min(fulltrack12$UTC),
                         end = max(fulltrack12$UTC), fill = NA, color = "white")

combined.g <- g1
combined.g$layers <- c(combined.g$layers, g2$layers)
#####
t1 <- plotTimeseries(fulltrack12, column='TOL_2000', bin='1hour', style = 'heatmap', title='Buoy 12: TOL 2000 Plot + ZC')
t2 <- plotPresGrid(W.12, bin = 'hour', type = 'presence', start = min(fulltrack12$UTC),
                         end = max(fulltrack12$UTC), fill = NA, color = "white")

@@

```{r fig.width=12}
## Buoy 13
W.13 <- fulltrack13 %>%
  select(UTC, BWpresence, species) %>%
  filter(species == "ZC")

@@

g1 <- (plotTimeseries(fulltrack13, column='TOL_125', bin='1hour', style = 'heatmap', title='Buoy 13: TOL 125 Plot + ZC'))
g2 <- plotPresGrid(W.13, bin = 'hour', type = 'presence', start = min(fulltrack13$UTC),
                         end = max(fulltrack13$UTC), fill = NA, color = "white")

combined.g <- g1
combined.g$layers <- c(combined.g$layers, g2$layers)
#####
t1 <- plotTimeseries(fulltrack13, column='TOL_2000', bin='1hour', style = 'heatmap', title='Buoy 13: TOL 2000 Plot + ZC')
t2 <- plotPresGrid(W.13, bin = 'hour', type = 'presence', start = min(fulltrack13$UTC),
                         end = max(fulltrack13$UTC), fill = NA, color = "white")

@@

```{r fig.width=12}
## Buoy 14
W.14 <- fulltrack14 %>%
  select(UTC, BWpresence, species) %>%
  filter(species == "ZC")

@@

g1 <- (plotTimeseries(fulltrack14, column='TOL_125', bin='hour', style = 'heatmap', title='Buoy 14: TOL 125 Plot + ZC'))
g2 <- plotPresGrid(W.14, bin = 'hour', type = 'presence', start = min(fulltrack14$UTC),
                         end = max(fulltrack14$UTC), fill = NA, color = "white")

combined.g <- g1
combined.g$layers <- c(combined.g$layers, g2$layers)
#####
t1 <- plotTimeseries(fulltrack14, column='TOL_2000', bin='hour', style = 'heatmap', title='Buoy 14: TOL 2000 Plot + ZC')
t2 <- plotPresGrid(W.14, bin = 'hour', type = 'presence', start = min(fulltrack14$UTC),
                         end = max(fulltrack14$UTC), fill = NA, color = "white")

@@

```{r fig.width=12}
## Buoy 16
W.16 <- fulltrack16 %>%
  select(UTC, BWpresence, species) %>%
  filter(species == "ZC")

@@

g1 <- (plotTimeseries(fulltrack16, column='TOL_125', bin='1hour', style = 'heatmap', title='Buoy 16: TOL 125 Plot + ZC'))
g2 <- plotPresGrid(W.16, bin = 'hour', type = 'presence', start = min(fulltrack16$UTC),
                         end = max(fulltrack16$UTC), fill = NA, color = "white")

combined.g <- g1
combined.g$layers <- c(combined.g$layers, g2$layers)
#####
t1 <- plotTimeseries(fulltrack16, column='TOL_2000', bin='1hour', style = 'heatmap', title='Buoy 16: TOL 2000 Plot + ZC')
t2 <- plotPresGrid(W.16, bin = 'hour', type = 'presence', start = min(fulltrack16$UTC),
                         end = max(fulltrack16$UTC), fill = NA, color = "white")

@@

```{r fig.width=12}
## Buoy 18
W.18 <- fulltrack18 %>%
  select(UTC, BWpresence, species) %>%
  filter(species == "ZC")

@@

g1 <- (plotTimeseries(fulltrack18, column='TOL_125', bin='1hour', style = 'heatmap', title='Buoy 18: TOL 125 Plot + ZC'))
g2 <- plotPresGrid(W.18, bin = 'hour', type = 'presence', start = min(fulltrack18$UTC),
                         end = max(fulltrack18$UTC), fill = NA, color = "white")

combined.g <- g1
combined.g$layers <- c(combined.g$layers, g2$layers)
#####
t1 <- plotTimeseries(fulltrack18, column='TOL_2000', bin='1hour', style = 'heatmap', title='Buoy 18: TOL 2000 Plot + ZC')
t2 <- plotPresGrid(W.18, bin = 'hour', type = 'presence', start = min(fulltrack18$UTC),
                         end = max(fulltrack18$UTC), fill = NA, color = "white")

@@

```{r fig.width=12}
## Buoy 19
W.19 <- fulltrack19 %>%
  select(UTC, BWpresence, species) %>%
  filter(species == "ZC")

@@

g1 <- (plotTimeseries(fulltrack19, column='TOL_125', bin='1hour', style = 'heatmap', title='Buoy 19: TOL 125 Plot + ZC'))
g2 <- plotPresGrid(W.19, bin = 'hour', type = 'presence', start = min(fulltrack19$UTC),
                         end = max(fulltrack19$UTC), fill = NA, color = "white")

combined.g <- g1
combined.g$layers <- c(combined.g$layers, g2$layers)
#####
t1 <- plotTimeseries(fulltrack19, column='TOL_2000', bin='1hour', style = 'heatmap', title='Buoy 19: TOL 2000 Plot + ZC')
t2 <- plotPresGrid(W.19, bin = 'hour', type = 'presence', start = min(fulltrack19$UTC),
                         end = max(fulltrack19$UTC), fill = NA, color = "white")

@@

```{r fig.width=12}
## Buoy 20
W.20 <- fulltrack20 %>%
  select(UTC, BWpresence, species) %>%
  filter(species == "ZC")

@@

g1 <- (plotTimeseries(fulltrack20, column='TOL_125', bin='1hour', style = 'heatmap', title='Buoy 20: TOL 125 Plot + ZC'))
g2 <- plotPresGrid(W.20, bin = 'hour', type = 'presence', start = min(fulltrack20$UTC),
                         end = max(fulltrack20$UTC), fill = NA, color = "white")

combined.g <- g1
combined.g$layers <- c(combined.g$layers, g2$layers)
#####
t1 <- plotTimeseries(fulltrack20, column='TOL_2000', bin='1hour', style = 'heatmap', title='Buoy 20: TOL 2000 Plot + ZC')
t2 <- plotPresGrid(W.20, bin = 'hour', type = 'presence', start = min(fulltrack20$UTC),
                         end = max(fulltrack20$UTC), fill = NA, color = "white")

@@

```{r fig.width=12}
## Buoy 21
W.21 <- fulltrack21 %>%
  select(UTC, BWpresence, species) %>%
  filter(species == "ZC")

@@

g1 <- (plotTimeseries(fulltrack21, column='TOL_125', bin='1hour', style = 'heatmap', title='Buoy 21: TOL 125 Plot + ZC'))
g2 <- plotPresGrid(W.21, bin = 'hour', type = 'presence', start = min(fulltrack21$UTC),
                         end = max(fulltrack21$UTC), fill = NA, color = "white")

combined.g <- g1
combined.g$layers <- c(combined.g$layers, g2$layers)
#####
t1 <- plotTimeseries(fulltrack21, column='TOL_2000', bin='1hour', style = 'heatmap', title='Buoy 21: TOL 2000 Plot + ZC')
t2 <- plotPresGrid(W.21, bin = 'hour', type = 'presence', start = min(fulltrack21$UTC),
                         end = max(fulltrack21$UTC), fill = NA, color = "white")

@@

```{r fig.width=12}
## Buoy 12
W.22 <- fulltrack22 %>%
  select(UTC, BWpresence, species) %>%
  filter(species == "ZC")

@@

g1 <- (plotTimeseries(fulltrack22, column='TOL_125', bin='1hour', style = 'heatmap', title='Buoy 22: TOL 125 Plot + ZC'))
g2 <- plotPresGrid(W.22, bin = 'hour', type = 'presence', start = min(fulltrack22$UTC),
                         end = max(fulltrack22$UTC), fill = NA, color = "white")

combined.g <- g1
combined.g$layers <- c(combined.g$layers, g2$layers)
#####
t1 <- plotTimeseries(fulltrack22, column='TOL_2000', bin='1hour', style = 'heatmap', title='Buoy 22: TOL 2000 Plot + ZC')
t2 <- plotPresGrid(W.22, bin = 'hour', type = 'presence', start = min(fulltrack22$UTC),
                         end = max(fulltrack22$UTC), fill = NA, color = "white")

@@

```{r fig.width=12}
## Buoy 23
W.23 <- fulltrack23 %>%
  select(UTC, BWpresence, species) %>%
  filter(species == "ZC")

@@

g1 <- (plotTimeseries(fulltrack23, column='TOL_125', bin='1hour', style = 'heatmap', title='Buoy 23: TOL 125 Plot + ZC'))
g2 <- plotPresGrid(W.23, bin = 'hour', type = 'presence', start = min(fulltrack23$UTC),
                         end = max(fulltrack23$UTC), fill = NA, color = "white")

>>>>

# 10th, 50th (mean), and 90th Percentiles

@@

@@

@@

Buoy 14 # Issue binding pct50 with others due to differing number of rows
```{r}
# 50th Percentile for Buoy 14 was calculated later and somehow has a differing number of rows with slightly different UTCs
# To allow for a cbind, I add two rows that are missing and use NAs for soundscape metrics.

# Create columns with percentiles and BIND
pct50_14_select <- pct50_14 %>% select(UTC, TOL_125, TOL_2000) %>% 
  rename(pct50_TOL125 = TOL_125,
         pct50_TOL2000 = TOL_2000)
pct10_14_select <- pct10_14 %>% select(UTC, TOL_125, TOL_2000) %>%
   rename(pct10_TOL125 = TOL_125,
         pct10_TOL2000 = TOL_2000)
pct90_14_select <- pct90_14 %>% select(UTC, TOL_125, TOL_2000) %>%
   rename(pct90_TOL125 = TOL_125,
         pct90_TOL2000 = TOL_2000)

# Remove last two rows of pct50_14_select in order to bind.
pct50_14_select <- pct50_14_select[1:1979,]

# Bind
pct14 <- cbind(pct10_14_select, pct50_14_select, pct90_14_select)

@@

#Summarize
buoy23pctSummary <- pct23_whl %>%
  group_by(species) %>%
  summarize(pct10_125_mean = mean(pct10_TOL125),
            pct50_125_mean = mean(pct50_TOL125),
            pct90_125_mean = mean(pct90_TOL125),
            pct10_2000_mean = mean(pct10_TOL2000),
            pct50_2000_mean = mean(pct50_TOL2000),
            pct90_2000_mean = mean(pct90_TOL2000))

ggplot(buoy23pctSummary) + geom_bar(aes(x = species))
```

@@

## Buoy 14 ##
sumPct14 <- kable(buoy14pctSummary, col.names = c("Animal", "10th", "Mean", "90th", "10th", "Mean", "90th"),
                                     caption = "Summary Percentiles for Buoy 14") %>%
  kableExtra::kable_classic() %>%
  kableExtra::add_header_above(c(" " = 1, "TOL 125" = 3, "TOL 2000" = 3))

@@

#pdf(paste("timeSeries8-31",".pdf"), width=14, height=10)

### Buoy 7 ####
W.07 <- GPSwhaleAISenvSS07 %>%
  select(UTC, Wpresence, species) %>%
  filter(species == "ZC")

@@

g1 <- (plotTimeseries(GPSwhaleAISenvSS07, column='TOL_125', bin='1hour', style = 'heatmap', title='Buoy 7: TOL 125 Plot + ZC'))
g2 <- plotPresGrid(W.07, bin = 'hour', type = 'presence', start = min(GPSwhaleAISenvSS07$UTC),
                         end = max(GPSwhaleAISenvSS07$UTC), fill = NA, color = "white")

@@

t1 <- plotTimeseries(GPSwhaleAISenvSS07, column='TOL_2000', bin='1hour', style = 'heatmap', title='Buoy 7: TOL 2000 Plot + ZC')
t2 <- plotPresGrid(W.07, bin = 'hour', type = 'presence', start = min(GPSwhaleAISenvSS07$UTC),
                         end = max(GPSwhaleAISenvSS07$UTC), fill = NA, color = "white")

@@

```{r fig.width=12}
###### Buoy 8 ####
W.08 <- GPSwhaleAISenvSS08 %>%
  select(UTC, Wpresence, species) %>%
  filter(species == "PM")

@@

g1 <- (plotTimeseries(GPSwhaleAISenvSS08, column='TOL_125', bin='1hour', style = 'heatmap', title='Buoy 8: TOL 125 Plot + PM'))
g2 <- plotPresGrid(W.08, bin = 'hour', type = 'presence', start = min(GPSwhaleAISenvSS08$UTC),
                         end = max(GPSwhaleAISenvSS08$UTC), fill = NA, color = "white")

combined.g <- g1
combined.g$layers <- c(combined.g$layers, g2$layers)
#####
t1 <- plotTimeseries(GPSwhaleAISenvSS08, column='TOL_2000', bin='1hour', style = 'heatmap', title='Buoy 8: TOL 2000 Plot + PM')
t2 <- plotPresGrid(W.08, bin = 'hour', type = 'presence', start = min(GPSwhaleAISenvSS08$UTC),
                         end = max(GPSwhaleAISenvSS08$UTC), fill = NA, color = "white")

@@

W.10 <- GPSwhaleAISenvSS10 %>%
  select(UTC, Wpresence, species) %>%
  filter(species == "PM")

@@

g1 <- (plotTimeseries(GPSwhaleAISenvSS10, column='TOL_125', bin='1hour', style = 'heatmap', title='Buoy 10: TOL 125 Plot + PM'))
g2 <- plotPresGrid(W.10, bin = 'hour', type = 'presence', start = min(GPSwhaleAISenvSS10$UTC),
                         end = max(GPSwhaleAISenvSS10$UTC), fill = NA, color = "white")

combined.g <- g1
combined.g$layers <- c(combined.g$layers, g2$layers)
#####
t1 <- plotTimeseries(GPSwhaleAISenvSS10, column='TOL_2000', bin='1hour', style = 'heatmap', title='Buoy 10: TOL 2000 Plot + PM')
t2 <- plotPresGrid(W.10, bin = 'hour', type = 'presence', start = min(GPSwhaleAISenvSS10$UTC),
                         end = max(GPSwhaleAISenvSS10$UTC), fill = NA, color = "white")

@@

```{r fig.width=12}
## Buoy 12
W.12 <- GPSwhaleAISenvSS12 %>%
  select(UTC, Wpresence, species) %>%
  filter(species == "PM")

@@

g1 <- (plotTimeseries(GPSwhaleAISenvSS12, column='TOL_125', bin='1hour', style = 'heatmap', title='Buoy 12: TOL 125 Plot + PM'))
g2 <- plotPresGrid(W.12, bin = 'hour', type = 'presence', start = min(GPSwhaleAISenvSS12$UTC),
                         end = max(GPSwhaleAISenvSS12$UTC), fill = NA, color = "white")

combined.g <- g1
combined.g$layers <- c(combined.g$layers, g2$layers)
#####
t1 <- plotTimeseries(GPSwhaleAISenvSS12, column='TOL_2000', bin='1hour', style = 'heatmap', title='Buoy 12: TOL 2000 Plot + PM')
t2 <- plotPresGrid(W.12, bin = 'hour', type = 'presence', start = min(GPSwhaleAISenvSS12$UTC),
                         end = max(GPSwhaleAISenvSS12$UTC), fill = NA, color = "white")

@@

```{r fig.width=12}
## Buoy 13
W.13 <- GPSwhaleAISenvSS13 %>%
  select(UTC, Wpresence, species) %>%
  filter(species == "ZC")

@@

g1 <- (plotTimeseries(GPSwhaleAISenvSS13, column='TOL_125', bin='1hour', style = 'heatmap', title='Buoy 13: TOL 125 Plot + ZC'))
g2 <- plotPresGrid(W.13, bin = 'hour', type = 'presence', start = min(GPSwhaleAISenvSS13$UTC),
                         end = max(GPSwhaleAISenvSS13$UTC), fill = NA, color = "white")

combined.g <- g1
combined.g$layers <- c(combined.g$layers, g2$layers)
#####
t1 <- plotTimeseries(GPSwhaleAISenvSS13, column='TOL_2000', bin='1hour', style = 'heatmap', title='Buoy 13: TOL 2000 Plot + ZC')
t2 <- plotPresGrid(W.13, bin = 'hour', type = 'presence', start = min(GPSwhaleAISenvSS13$UTC),
                         end = max(GPSwhaleAISenvSS13$UTC), fill = NA, color = "white")

@@

```{r fig.width=12}
## Buoy 14
W.14 <- GPSwhaleAISenvSS14 %>%
  select(UTC, Wpresence, species) %>%
  filter(species == "PM")

@@

g1 <- (plotTimeseries(GPSwhaleAISenvSS14, column='TOL_125', bin='hour', style = 'heatmap', title='Buoy 14: TOL 125 Plot + PM'))
g2 <- plotPresGrid(W.14, bin = 'hour', type = 'presence', start = min(GPSwhaleAISenvSS14$UTC),
                         end = max(GPSwhaleAISenvSS14$UTC), fill = NA, color = "white")

combined.g <- g1
combined.g$layers <- c(combined.g$layers, g2$layers)
#####
t1 <- plotTimeseries(GPSwhaleAISenvSS14, column='TOL_2000', bin='hour', style = 'heatmap', title='Buoy 14: TOL 2000 Plot + PM')
t2 <- plotPresGrid(W.14, bin = 'hour', type = 'presence', start = min(GPSwhaleAISenvSS14$UTC),
                         end = max(GPSwhaleAISenvSS14$UTC), fill = NA, color = "white")

@@

```{r fig.width=12}
## Buoy 16
W.16 <- GPSwhaleAISenvSS16 %>%
  select(UTC, Wpresence, species) %>%
  filter(species == "ZC")

@@

g1 <- (plotTimeseries(GPSwhaleAISenvSS16, column='TOL_125', bin='1hour', style = 'heatmap', title='Buoy 16: TOL 125 Plot + ZC'))
g2 <- plotPresGrid(W.16, bin = 'hour', type = 'presence', start = min(GPSwhaleAISenvSS16$UTC),
                         end = max(GPSwhaleAISenvSS16$UTC), fill = NA, color = "white")

combined.g <- g1
combined.g$layers <- c(combined.g$layers, g2$layers)
#####
t1 <- plotTimeseries(GPSwhaleAISenvSS16, column='TOL_2000', bin='1hour', style = 'heatmap', title='Buoy 16: TOL 2000 Plot + ZC')
t2 <- plotPresGrid(W.16, bin = 'hour', type = 'presence', start = min(GPSwhaleAISenvSS16$UTC),
                         end = max(GPSwhaleAISenvSS16$UTC), fill = NA, color = "white")

@@

```{r fig.width=12}
## Buoy 18
W.18 <- GPSwhaleAISenvSS18 %>%
  select(UTC, Wpresence, species) %>%
  filter(species == "ZC")

@@

g1 <- (plotTimeseries(GPSwhaleAISenvSS18, column='TOL_125', bin='1hour', style = 'heatmap', title='Buoy 18: TOL 125 Plot + ZC'))
g2 <- plotPresGrid(W.18, bin = 'hour', type = 'presence', start = min(GPSwhaleAISenvSS18$UTC),
                         end = max(GPSwhaleAISenvSS18$UTC), fill = NA, color = "white")

combined.g <- g1
combined.g$layers <- c(combined.g$layers, g2$layers)
#####
t1 <- plotTimeseries(GPSwhaleAISenvSS18, column='TOL_2000', bin='1hour', style = 'heatmap', title='Buoy 18: TOL 2000 Plot + ZC')
t2 <- plotPresGrid(W.18, bin = 'hour', type = 'presence', start = min(GPSwhaleAISenvSS18$UTC),
                         end = max(GPSwhaleAISenvSS18$UTC), fill = NA, color = "white")

@@

```{r fig.width=12}
## Buoy 19
W.19 <- GPSwhaleAISenvSS19 %>%
  select(UTC, Wpresence, species) %>%
  filter(species == "ZC")

@@

g1 <- (plotTimeseries(GPSwhaleAISenvSS19, column='TOL_125', bin='1hour', style = 'heatmap', title='Buoy 19: TOL 125 Plot + ZC'))
g2 <- plotPresGrid(W.19, bin = 'hour', type = 'presence', start = min(GPSwhaleAISenvSS19$UTC),
                         end = max(GPSwhaleAISenvSS19$UTC), fill = NA, color = "white")

combined.g <- g1
combined.g$layers <- c(combined.g$layers, g2$layers)
#####
t1 <- plotTimeseries(GPSwhaleAISenvSS19, column='TOL_2000', bin='1hour', style = 'heatmap', title='Buoy 19: TOL 2000 Plot + ZC')
t2 <- plotPresGrid(W.19, bin = 'hour', type = 'presence', start = min(GPSwhaleAISenvSS19$UTC),
                         end = max(GPSwhaleAISenvSS19$UTC), fill = NA, color = "white")

@@

```{r fig.width=12}
## Buoy 20
W.20 <- GPSwhaleAISenvSS20 %>%
  select(UTC, Wpresence, species) %>%
  filter(species == "ZC")

@@

g1 <- (plotTimeseries(GPSwhaleAISenvSS20, column='TOL_125', bin='1hour', style = 'heatmap', title='Buoy 20: TOL 125 Plot + ZC'))
g2 <- plotPresGrid(W.20, bin = 'hour', type = 'presence', start = min(GPSwhaleAISenvSS20$UTC),
                         end = max(GPSwhaleAISenvSS20$UTC), fill = NA, color = "white")

combined.g <- g1
combined.g$layers <- c(combined.g$layers, g2$layers)
#####
t1 <- plotTimeseries(GPSwhaleAISenvSS20, column='TOL_2000', bin='1hour', style = 'heatmap', title='Buoy 20: TOL 2000 Plot + ZC')
t2 <- plotPresGrid(W.20, bin = 'hour', type = 'presence', start = min(GPSwhaleAISenvSS20$UTC),
                         end = max(GPSwhaleAISenvSS20$UTC), fill = NA, color = "white")

@@

```{r fig.width=12}
## Buoy 21
W.21 <- GPSwhaleAISenvSS21 %>%
  select(UTC, Wpresence, species) %>%
  filter(species == "ZC")

@@

g1 <- (plotTimeseries(GPSwhaleAISenvSS21, column='TOL_125', bin='1hour', style = 'heatmap', title='Buoy 21: TOL 125 Plot + ZC'))
g2 <- plotPresGrid(W.21, bin = 'hour', type = 'presence', start = min(GPSwhaleAISenvSS21$UTC),
                         end = max(GPSwhaleAISenvSS21$UTC), fill = NA, color = "white")

combined.g <- g1
combined.g$layers <- c(combined.g$layers, g2$layers)
#####
t1 <- plotTimeseries(GPSwhaleAISenvSS21, column='TOL_2000', bin='1hour', style = 'heatmap', title='Buoy 21: TOL 2000 Plot + ZC')
t2 <- plotPresGrid(W.21, bin = 'hour', type = 'presence', start = min(GPSwhaleAISenvSS21$UTC),
                         end = max(GPSwhaleAISenvSS21$UTC), fill = NA, color = "white")

@@

```{r fig.width=12}
## Buoy 22
W.22 <- GPSwhaleAISenvSS22 %>%
  select(UTC, Wpresence, species) %>%
  filter(species == "PM")

@@

g1 <- (plotTimeseries(GPSwhaleAISenvSS22, column='TOL_125', bin='1hour', style = 'heatmap', title='Buoy 22: TOL 125 Plot + ZC'))
g2 <- plotPresGrid(W.22, bin = 'hour', type = 'presence', start = min(GPSwhaleAISenvSS22$UTC),
                         end = max(GPSwhaleAISenvSS22$UTC), fill = NA, color = "white")

combined.g <- g1
combined.g$layers <- c(combined.g$layers, g2$layers)
#####
t1 <- plotTimeseries(GPSwhaleAISenvSS22, column='TOL_2000', bin='1hour', style = 'heatmap', title='Buoy 22: TOL 2000 Plot + ZC')
t2 <- plotPresGrid(W.22, bin = 'hour', type = 'presence', start = min(GPSwhaleAISenvSS22$UTC),
                         end = max(GPSwhaleAISenvSS22$UTC), fill = NA, color = "white")

@@

```{r fig.width=12}
## Buoy 23
W.23 <- GPSwhaleAISenvSS23 %>%
  select(UTC, Wpresence, species) %>%
  filter(species == "ZC")

@@

g1 <- (plotTimeseries(GPSwhaleAISenvSS23, column='TOL_125', bin='1hour', style = 'heatmap', title='Buoy 23: TOL 125 Plot + ZC'))
g2 <- plotPresGrid(W.23, bin = 'hour', type = 'presence', start = min(GPSwhaleAISenvSS23$UTC),
                         end = max(GPSwhaleAISenvSS23$UTC), fill = NA, color = "white")
